\documentclass{article}
\usepackage[utf8]{inputenc}

\title{data_science_decal_syllabus}
\author{johannes.kukula }
\date{September 2018}

\begin{document}

\section*{Assignments and Grading}
	The class is graded on a Pass / No Pass system and counts two units towards your Harry Potter expert degree. A minimum of 70 \% must be achieved in order to pass the class. 
	The grade is based upon the following: 

\subsection*{Attendance and Participation - 40 \%}	
	Attendance is absolutely crucial toward your success in this class. Roll will be taken during every class. If you come late or leave early without a good reason, you will be docked points. Each week the first half of class will consist of a combination of lecture and discussion relating to the week’s reading. The second half of each class period will be a fun activity related to the week’s reading or the series as a whole. We will also have weekly assignments.

\subsection*{Weekly Reading Quizzes - 10 \%}
    There will be a short reading quiz every class.
	
\subsection*{Written Reflection - 15 \%}		
	This is just a two-page, double-spaced response to the series and the secondary readings. You will be asked to make connections between concepts in the books and concepts in these articles, using your own interpretation of the readings (this means this is no *right* answer, we’re just looking for some original thinking). Reflection questions will be distributed two weeks before the due date (see syllabus).

\subsection*{Final Project - 15 \%}		
    In lieu of a final, you will have a final project. You must submit a project proposal to the instructors by December 1st. More information concerning this project will be passed out a few weeks before it is due. The final project is your own creative interpretation of the material covered throughout the course.  It can be whatever you want: a story written in the world of Harry Potter, an illustration of some sort, a video, a game, or performance art – anything you like so long as it meets two conditions.  The first is that you must relate it fairly explicitly to the course material. The second is that you must put some time into it; although we aren't expecting a drawing of yours to be worthy of the Louvre, we nevertheless will refuse to accept something obviously drawn in the ten minutes before class. You are allowed to work in a group. Final projects will not be accepted late – barring grave circumstances (emphasis on “grave”), no exceptions to this rule will be granted. Don’t stress about this – the idea is that you put effort into it because you really like what you’re doing.

\end{document}
