\documentclass{article}
\usepackage[utf8]{inputenc}

\title{The Wonderful Wizarding World of Harry Potter Decal Syllabus}
\author{Fall 2018}
\date{ }
\begin{document}

 \maketitle

\section{Course Overview }
In this course you will explore J.K. Rowling’s world in the Harry Potter series by book discussions and relevant activities. We will also explore the genre of fantasy by analyzing the topics, themes, and issues shown throughout the book. Additionally, we will see what has made it the best-selling book series of all time. We hope to prove that Harry Potter is a work of academic merit to our students. To do this, we will discuss:
\begin{enumerate}
\item the history of magic, witchcraft, and wizardry
\item social hierarchies and the role of race in culture 
\item the social relationships and dynamics: friendships and families
\item international education and cooperation 
\item the role of government and corruption, concentration on authoritarianism, in civilian life
\item children’s literature, fantasy novels and the Harry Potter fandom
\item the role of death and love in the hero’s journey
\end{enumerate}

This class is open to everyone, however we have lifted our spoiler ban, meaning text spoilers are allowed in class! If you are a first-time reader, you are welcome regardless, but be prepared! At times, our faculty advisor will also attend lecture as part of their supervision and sponsorship of our class.

\maketitle

\section{General Overview}
 The class is split into two parts. The first part is a discussion, a reading quiz, and a short lecture based on that week's reading. The second is a fun activity based on that week's reading, for which you can win points for your house toward the illustrious House Cup. Points will also be awarded for bringing in food (extra for homemade or Harry Potter themed food!)
 
\subsection {Required Readings}

\begin{enumerate}
\item Harry Potter and the Philosopher’s Stone
\item Harry Potter and the Chamber of Secrets
\item Harry Potter and the Prisoner of Azkaban
\item Harry Potter and the Goblet of Fire
\item Harry Potter and the Order of the Phoenix
\item Harry Potter and the Half-Blood Prince
\end{enumerate}

Additional readings and multimedia resources will be available to you online.
Do not be discouraged by the book list. Each book can easily been read in less than one day, so it will not be hard to finish reading them throughout the semester. These books will be fun to read, so don’t be surprised if you finish them all sooner than expected!
\end{document}

