\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }
\title{The Wonderful Wizarding World of Harry Potter Decal Syllabus}
\author{Fall 2018}
\date{ }
\begin{document}

 \maketitle

\section{Course Overview }
In this course you will explore J.K. Rowling’s world in the Harry Potter series by book discussions and relevant activities. We will also explore the genre of fantasy by analyzing the topics, themes, and issues shown throughout the book. Additionally, we will see what has made it the best-selling book series of all time. We hope to prove that Harry Potter is a work of academic merit to our students. To do this, we will discuss:
\begin{enumerate}
\item the history of magic, witchcraft, and wizardry
\item social hierarchies and the role of race in culture 
\item the social relationships and dynamics: friendships and families
\item international education and cooperation 
\item the role of government and corruption, concentration on authoritarianism, in civilian life
\item children’s literature, fantasy novels and the Harry Potter fandom
\item the role of death and love in the hero’s journey
\end{enumerate}

This class is open to everyone, however we have lifted our spoiler ban, meaning text spoilers are allowed in class! If you are a first-time reader, you are welcome regardless, but be prepared! At times, our faculty advisor will also attend lecture as part of their supervision and sponsorship of our class.

\maketitle

\section{General Overview}
 The class is split into two parts. The first part is a discussion, a reading quiz, and a short lecture based on that week's reading. The second is a fun activity based on that week's reading, for which you can win points for your house toward the illustrious House Cup. Points will also be awarded for bringing in food (extra for homemade or Harry Potter themed food!)
 
\subsection {Required Readings}

\begin{enumerate}
\item Harry Potter and the Philosopher’s Stone
\item Harry Potter and the Chamber of Secrets
\item Harry Potter and the Prisoner of Azkaban
\item Harry Potter and the Goblet of Fire
\item Harry Potter and the Order of the Phoenix
\item Harry Potter and the Half-Blood Prince
\end{enumerate}

Additional readings and multimedia resources will be available to you online.
Do not be discouraged by the book list. Each book can easily been read in less than one day, so it will not be hard to finish reading them throughout the semester. These books will be fun to read, so don’t be surprised if you finish them all sooner than expected!

\section*{Assignments and Grading}
	The class is graded on a Pass / No Pass system and counts two units towards your Harry Potter expert degree. A minimum of 70 \% must be achieved in order to pass the class. 
	The grade is based upon the following: 

\subsection*{Attendance and Participation - 40 \%}	
	Attendance is absolutely crucial toward your success in this class. Roll will be taken during every class. If you come late or leave early without a good reason, you will be docked points. Each week the first half of class will consist of a combination of lecture and discussion relating to the week’s reading. The second half of each class period will be a fun activity related to the week’s reading or the series as a whole. We will also have weekly assignments.

\subsection*{Weekly Reading Quizzes - 10 \%}
    There will be a short reading quiz every class.
	
\subsection*{Written Reflection - 15 \%}		
	This is just a two-page, double-spaced response to the series and the secondary readings. You will be asked to make connections between concepts in the books and concepts in these articles, using your own interpretation of the readings (this means this is no *right* answer, we’re just looking for some original thinking). Reflection questions will be distributed two weeks before the due date (see syllabus).

\subsection*{Final Project - 15 \%}		
    In lieu of a final, you will have a final project. You must submit a project proposal to the instructors by December 1st. More information concerning this project will be passed out a few weeks before it is due. The final project is your own creative interpretation of the material covered throughout the course.  It can be whatever you want: a story written in the world of Harry Potter, an illustration of some sort, a video, a game, or performance art – anything you like so long as it meets two conditions.  The first is that you must relate it fairly explicitly to the course material. The second is that you must put some time into it; although we aren't expecting a drawing of yours to be worthy of the Louvre, we nevertheless will refuse to accept something obviously drawn in the ten minutes before class. You are allowed to work in a group. Final projects will not be accepted late – barring grave circumstances (emphasis on “grave”), no exceptions to this rule will be granted. Don’t stress about this – the idea is that you put effort into it because you really like what you’re doing.

\begin{table} [h!]
\begin{large}


\begin{center}
\textbf{Harry Potter Decal Schedule}
\begin{tabular}{c|c|c} 
      \textbf{Class Week} & \textbf{Topics} & \textbf{Assignments}\\
      \hline
      8/26 & Course Introduction and Syllabus Explanation & Show up to first class\\
      \hline
      9/2 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Sorcerer's Stone} \\ Magic, Witchcraft, Wizardry \\ \textbf{ History of Sorting and Witchcraft}\end{tabular} & Book 1\\
      \hline
      9/9 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Chamber of Secrets} \\ Social Class, Racial Issues \\ \textbf{ How to Make a Wand}\end{tabular} & Book 2\\
      \hline
      9/16 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Prisoner of Azkaban} \\ Legal Systems in the Wizard's World \\ \textbf{Politics in the World of Wizardry}\end{tabular} & Book 3\\
      \hline
      9/23 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Goblet of Fire} \\ International Magical Corporation \\ \textbf{Wizard Tournament}\end{tabular} & Book 4\\
      \hline
      9/30 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and Goblet of Fire} \\ Education and Different Wizardry Institutions \\ \textbf{History of Wizardry Education}\end{tabular} & Book 4\\
      \hline
      10/7 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Order of Phoenix} \\ Quidditch \\ \textbf{ How to Play Quidditch}\end{tabular} & Book 5\\
      \hline
      10/14 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Order of Phoenix} \\ Government \& Civilian's Life in the World of Magic \\ \textbf{ Character Trivia}\end{tabular} & Book 5\\
      \hline
      10/21 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Order of Phoenix} \\ Quidditch \\ \textbf{ How to Play Quidditch}\end{tabular} & Book 5\\
      \hline
      10/28 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Half-Blood Prince} \\ The Harry Potter Phenomenon \\ \textbf{Jeopardy}\end{tabular} & Book 6\\
      \hline
      11/4 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Half-Blood Prince} \\ Danger and Trust \\ \textbf{Discussions of Additional Readings}\end{tabular} & Book 6\\
      \hline
      11/11 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Deathly Hallows} \\ The Light and the Dark\\ \textbf{Interpretation of the Book V.S. the Movie}\end{tabular} & Book 7\\
      \hline
      11/18 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Deathly Hallows} \\ The Role of Love in Harry Potter\\ \textbf{Reflections}\end{tabular} & Book 7\\
      \hline
      11/25 & \begin{tabular}{@{}c@{}}\textit{Harry Potter and the Deathly Hallows} \\ The Light and the Dark\\ \textbf{Interpretation of the Book V.S. the Movie}\end{tabular} & Book 7\\
      \hline
      12/2 & \begin{tabular}{@{}c@{}} Last Day of Class\\ Final Projects and Presentations\\Final Evaluations\end{tabular} & Team Project\\
      \hline


    \end{tabular}

\end{center}
\end{large}


\end{table}
\end{document}

